Transmembrane helices are an overlooked and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 frontiers.tex
Update keywords, fix Q9

\tiny
 \keyFont{ \section{Keywords:} antigen presentation, membrane proteins, bioinformatics, adaptive immunity, transmembrane domain, transmembrane helix, epitopes, T lymphocyte, MHC-I, MHC-II, evolutionary conservation}
\end{abstract}

>>>>

\tiny
 \keyFont{ \section{Keywords:} antigen presentation, membrane proteins,adaptive immunity, transmembrane domain, epitopes, MHC-I, MHC-II, evolutionary conservation}
\end{abstract}

### 2021-12-29 manuscript.tex
Fix typo, thanks Frans
Update keywords, fix Q9

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, evolutionary conservation

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_n_snps_per_tmp.png}
  \caption{
    Histogram of the number of SNPs per trans-membrane protein.
    Dashed vertical line: average number of SNPs per TMP
  }
  \label{fig:fig_n_snps_per_tmp}
\end{figure}

>>>>

{\bf Keywords:} antigen presentation, membrane proteins,adaptive immunity, transmembrane domain, epitopes, MHC-I, MHC-II, evolutionary conservation

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_n_snps_per_tmp.png}
  \caption{
    Histogram of the number of SNPs per trans-membrane protein.
  }
  \label{fig:fig_n_snps_per_tmp}
\end{figure}
